%-------------------------
% Resume in LaTeX
% Author: Byungjun Yoon
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{tabularx} % in the preamble
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.97\textwidth}[t]{Xr}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabularx}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[1]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
	\textbf{\Huge \scshape Byungjun Yoon} \\ \vspace{3pt}
	\small
	\faMobile \hspace{.5pt} \href{tel:821033093695}{+82 010 3309 3695}
	$|$
	\faAt \hspace{.5pt} \href{mailto:junyoon@postech.ac.kr}{junyoon@postech.ac.kr}
	$|$
	\faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/byungjun-yoon-43a766216/}{LinkedIn}
	$|$
	\faGithub \hspace{.5pt} \href{https://github.com/happyhappy-jun}{GitHub}
	$|$
	% \faGlobe \hspace{.5pt} \href{https://arasgungore.github.io}{Portfolio}
	% $|$
	\faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/seoul/data=!4m2!3m1!1s0x357ca2012d5c39cf:0x7e11eca1405bf29b?sa=X&ved=2ahUKEwi_6sKkyrGDAxUXklYBHVOADyAQ8gF6BAgQEAA}{Seoul, Korea}
\end{center}

%----------- EDUCATION -----------

\section{Research Interest}
\resumeSubHeadingListStart
\resumeItem{My research interest lies in various topics in \textbf{Machine Learning}, \textbf{Large Language Models}, and \textbf{their fundamentals, practical applications}. I am particularly interested in ML/AI topics that can enhance human productivity. Currently, the large language model and its factual content generation are my main focuses.}
\resumeSubHeadingListEnd

%----------- EDUCATION -----------

\section{Education}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeEducationHeading
{Pohang University of Science and Technology
}{Pohang, Korea}
{B.S. in Computer Science (GPA: 3.6/4.3, Major GPA: 3.8)}{Feb 2019 \textbf{--} Present}

\resumeEducationHeading
{McLean High School}
{Virginia, USA}
{}
{Sep 2015 \textbf{--} Jun 2018}

\resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Work}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{Devsisters}{Seoul, Korea}
{Applied Data Scientist, Software Engineer}
{Sep 2021 \textbf{--} Oct 2023, Full-time}
\resumeItemListStart
\resumeItem{Led the development of a Customer ROAS Prediction System as time-series prediction task for data-oriented UA marketing decisions.}
\resumeItem{Improved prediction speed of the legacy MCMC-based Life Time Value Model.}
\resumeItem{Implemented and maintained a PPO-based puzzle game automation RL agent.}
\resumeItem{Researched a log-based user churn prediction algorithm for Cookie Run: Kingdom.}
\resumeItem{Developed a distributed PyTorch dataloader wrapper for Parquet datasets in a distributed data environment.}
\resumeItem{Developed a front-end webpage with Next.js.}
\resumeItemListEnd

\resumeSubheading
{Naver Webtoon}{Pangyo, Korea}
{Research Intern, W-Tech Research Team: AI Automation}{Jun 2021 \textbf{--} Aug 2021, Internship}
\resumeItemListStart
\resumeItem{Researched an unsupervised clustering of webtoon drawing styles subject to deformation of human to provide benchmark for downstream ML tasks.}
\resumeItem{Researched a webtoon drawing style embedding model and similarity metrics based on a metric learning.}
\resumeItemListEnd

\resumeSubheading
{Reziena} {Seoul, Korea}
{Intern}
{Jun 2020 \textbf{--} Aug 2020, Internship}
\resumeItemListStart
\resumeItem{Researched the backend and ETL pipeline for data from IoT devices, developed a Skin Type Classification Algorithm, analyzed AWS Infra security, and implemented a Firebase authentication system.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- RESEARCH EXPERIENCE -----------

\section{Research}
\vspace{3pt}
\resumeSubHeadingListStart
\resumeSubheading
{Method for Enhancing retrieval-augmented generation by prompting model}
{DI Lab}
{Advisor: \href{https://sites.google.com/view/postechdi/member/faculty}{Hwanjo Yu}}
{Sep 2023 \textbf{--} Present, Internship}
\resumeItemListStart
\resumeItem{Researching a new RAG framework, which inserts a prompting model between a retriever model and a generator model to improve the RAG framework in a black-box frozen generator environment.}
\resumeItem{Preparing for the paper submission as a first author to top-tier conferences during 2024.}
\resumeItemListEnd

\resumeSubheading
{DARPA AI Cyber Challenge}
{Team Atlanta}
{Lead by Taesoo Kim @GaTech, Advised by Sangdon Park @MLLab}
{Sep 2023 \textbf{--} Present, ML Task Member}
\resumeItemListStart
\resumeItem{Working as a team member in Team Atlanta consist of SSLab@GaTech, Hacking Lab@KAIST, ML Lab@POSTECH, Samsung Researach, and others}
\resumeItem{Researching ML pipeline of automatic CVE patch (including vulnerability detection, patch generation)}
\resumeItemListEnd

\resumeSubheading
{Lung Abnormalities Detection}
{AIMI Lab}
{Advisor: \href{https://miv.postech.ac.kr/members/}{Wonhwa Kim}}
{Oct 2020 \textbf{--} Jun 2021, Internship}
\resumeItemListStart
\resumeItem{Researched lung abnormality detection in chest x-ray images using R50-FPN for localization and abnormality classification.}
\resumeItemListEnd

\resumeSubheading
{Undergraduate Research Participation}
{CV Lab}
{Advisor: \href{https://suhakwak.github.io/index.html}{Suha Kwak}}
{Dec 2020 \textbf{--} Feb 2021, Internship}
\resumeItemListStart
\resumeItem{Studied Metric Learning, Computer Vision, and CS231n.}
\resumeItem{Reproduced related papers: \href{https://arxiv.org/abs/1805.08974}{[1]}, \href{https://arxiv.org/abs/2010.01412}{[2]}.}

\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
	            \textbf{Technologies:} {PyTorch, PyMC, Pyro, Slurm, TensorFlow, PySpark, Git, Docker, Kubernetes, Helm, Next.js, React, Unity ML-Agent, Flask, Node.js }

	            \textbf{Languages:} {Python, Java, C/C++, JavaScript/TypeScript, Solidity, Rust} \\ \vspace{3pt}
	      }}
\resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
	            \textbf{1st Place Award in the Postech Open Innovation Big Data Challenge} \\ \vspace{3pt}
	      }}
\resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Deep Learning (CSED538) In-class Image Classification Competition} $|$ \emph{\href{https://github.com/happyhappy-jun/CSED538-final-project}{Github}}}
\resumeItemListStart
\resumeItem{Developed an image classification framework based on ViT and RandAugment}
\resumeItem{Achieved first place in the competition}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Personality Prediction AI and App Development} $|$ \emph{\href{https://github.com/hhyy0401/UGRP}{GitHub}}}
\resumeItemListStart
\resumeItem{Lead the model development process of vision model that classify a person's MBTI with vision models}
\resumeItem{Deployed a web application to serve our model in a web environment.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Solar Energy Prediction System} $|$ \emph{\href{https://github.com/happyhappy-jun/2020-Postech-Open-innovation-Bigdata-Challenge}{Github}}}
\resumeItemListStart
\resumeItem{Developed a multivariate time-series prediction model for predicting solar energy production}
\resumeItem{Received the First Place Award in the Postech Open Innovation Big Data Challenge}
\resumeItemListEnd
\resumeSubHeadingListEnd

%----------- RELEVANT COURSEWORK -----------

%----------- RELEVANT COURSEWORK -----------

\section{Relevant Coursework}
\vspace{3pt}
\resumeSubHeadingListStart
\small{\item{
	            \textbf{Major coursework:}{
		            Deep Learing (CSED538),
		            Deep Learning NLP (CSED554),
		            Implem. \& Accel. for Machine Learning (CSED510),
		            Software Design Methods (CSED332),
		            Artificial Intelligence (CSED342),
		            Data Analysis Using Tools (CSED490A),
		            Operating Systems (CSED312),
		            Computer Architecture (CSED311),
		            Automata \& Formal Languages (CSED341),
		            Algorithm (CSED331),
		            Object Oriented Programming (CSED232),
		            Data Structure (CSED233),
		            Discrete Math (CSED261),
		            Digital Sys. Design (CSED273),
		            Intro. to Computer SW Systems (CSED211),
		            Applied Linear Algebra (MATH203),
	            }
	      }}
\resumeSubHeadingListEnd

%----------- CERTIFICATES -----------

\section{Mentoring}
\vspace{3pt}
\resumeSubHeadingListStart
\small{
	\item {POSTECH Intro. to Artifical Intelligence (AIGS101) TA}
	\item {2nd POSTECH ON-LINE Hacking \& Cyber Security Camp Mentor}
	\item {5th POSTECH Computational Thinking Camp Mentor}
}
\resumeSubHeadingListEnd

%----------- ORGANIZATIONS -----------

\section{Organizations}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeOrganizationHeading
{PLUS (POSTECH Labatory for Unix Security)}{Aug 2019 -- Present}{Member}

\resumeOrganizationHeading
{PDAO (POSTECH Decentralized Autonomous Organization)} {Apr 2022 -- Present}{Committee Member}

\resumeSubHeadingListEnd

\section{Others}
\vspace{3pt}
\resumeSubHeadingListStart
\small{
	\item {TOEFL: 105/120 (2019)}
}
\resumeSubHeadingListEnd

%----------- HOBBIES -----------

% \section{Hobbies}
% \resumeSubHeadingListStart
% \small{\item{Swimming, Fitness, Eight-ball}}
% \resumeSubHeadingListEnd

%----------- REFERENCES -----------

% \section{References}
% \vspace{2pt}
% \resumeSubHeadingListStart
% \item{References available upon request.}
% \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
